Lasso_RCI_Response

### 2024-01-30 Lasso_RCI_Response.Rmd
Adding new RMD with stuff just for LAsso responder paper

---
title: "Paper_stuff"
output: html_document
date: "2023-09-12"
---

@@

Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
head(df)
```

## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
Mothership <- mutate(Mothership, 
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                          "0"="<Grade 12",
                          "1"="<Grade 12",
                          "2"="HS Diploma or GED",
                          "3"="HS Diploma or GED",
                          "4"="Some College/Associates Degree",
                          "5"="Some College/Associates Degree",
                          "6"="Bachelors Degree",
                          "7"="Bachelors Degree",
                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                          "0"="Female",
                          "1"="Male",
                          "2"="Non-Binary",
                          "3"="Other",
                          "4"="Other"),
                     Relationship_1 = ifelse(Relationship_1 == 8, NA, Relationship_1),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                          "0"="Married or Cohabitating",
                          "1"="Married or Cohabitating",
                          "2"="Widowed or Separated",
                          "3"="Widowed or Separated",
                          "4"="Divorced",
                          "5"="Single or Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                          "1"="Straight",
                          "2"="Gay",
                          "3"="Bisexual",
                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                          "0"="General",
                          "1"="Trauma",
                          "2"="Young Adult",
                          "3"="BPD"),
                     Race_1 = ifelse(Race_1 == 6, NA, Race_1),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1" ="Inpatient",
                                      "2" ="PHP",
                                      "3" ="APS",
                                      "4" ="Psychatrist",
                                      "5" ="PCP",
                                      "6" ="Another Physican",
                                      "7" ="Therapist",
                                      "8"="Withdrew (AMA)",
                                      "9"="Other",
                                      "10"="Other",
                                      "11"="Other",
                                      "17"="Other",
                                      "0" ="Other"),

@@

####. Disorder_variables

@@

          # co occuring disorders
                  Co_Anx = as.factor(
                        ifelse(Anxiety_C == 1 & Mood_D == 1 |
                                Anxiety_C == 1 & OCD_P == 1 |
                                Anxiety_C == 1 & BPD_P == 1 |
                                Anxiety_C == 1 & Substance_D == 1 |
                                Anxiety_C == 1 & Trauma_D == 1 |
                                Anxiety_C == 1 & Eating_D ==1 |
                                Anxiety_C == 1 & Psychotic_D ==1 |
                                Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_Mood = as.factor(
                        ifelse(Mood_C == 1 & Anxiety_D == 1 |
                                Mood_C == 1 & OCD_P == 1 |
                                Mood_C == 1 & BPD_P == 1 |
                                Mood_C == 1 & Substance_D == 1 |
                                Mood_C == 1 & Trauma_D == 1 |
                                Mood_C == 1 & Eating_D ==1 |
                                Mood_C == 1 & Psychotic_D ==1 |
                                Mood_C == 1 & Somatic_D==1 , 1, 0)),
                  Co_OCD = as.factor(
                        ifelse(OCD_C == 1 & Anxiety_D == 1 |
                                OCD_C == 1 & Mood_D == 1 |
                                OCD_C == 1 & BPD_P== 1 |
                                OCD_C == 1 & Substance_D == 1 |
                                OCD_C == 1 & Trauma_D == 1 |
                                OCD_C == 1 & Eating_D ==1 |
                                OCD_C == 1 & Psychotic_D ==1 |
                                OCD_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_BPD = as.factor(
                        ifelse(BPD_C == 1 & Anxiety_D == 1 |
                                BPD_C == 1 & Mood_D == 1 |
                                BPD_C == 1 & OCD_P== 1 |
                                BPD_C == 1 & Substance_D == 1 |
                                BPD_C == 1 & Trauma_D == 1 |
                                BPD_C == 1 & Eating_D ==1 |
                                BPD_C == 1 & Psychotic_D ==1 |
                                BPD_C == 1 & Somatic_D ==1 , 1, 0)),
                  Co_Psychotic = as.factor(
                       ifelse(Psychotic_C == 1 & Mood_D == 1 |
                                Psychotic_C == 1 & OCD_P == 1 |
                                Psychotic_C == 1 & BPD_P == 1 |
                                Psychotic_C == 1 & Substance_D == 1 |
                                Psychotic_C == 1 & Trauma_D == 1 |
                                Psychotic_C == 1 & Eating_D ==1 |
                                Psychotic_C == 1 & Anxiety_D ==1 |
                                Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_Eating = as.factor(
                      ifelse(Eating_C == 1 & Mood_D == 1 |
                                Eating_C == 1 & OCD_P == 1 |
                                Eating_C == 1 & BPD_P == 1 |
                                Eating_C == 1 & Substance_D == 1 |
                                Eating_C == 1 & Trauma_D == 1 |
                                Eating_C == 1 & Psychotic_D ==1 |
                                Eating_C == 1 & Anxiety_D ==1 |
                                Eating_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_Somatic =  as.factor(
                       ifelse(Somatic_C == 1 & Mood_D == 1 |
                                Somatic_C == 1 & OCD_P == 1 |
                                Somatic_C == 1 & BPD_P == 1 |
                                Somatic_C == 1 & Substance_D == 1 |
                                Somatic_C == 1 & Trauma_D == 1 |
                                Somatic_C == 1 & Eating_D ==1 |
                                Somatic_C == 1 & Anxiety_D ==1 |
                                Somatic_C == 1 & Substance_D ==1 |
                                Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
                  Co_Substance = as.factor(
                      ifelse(Substance_C == 1 & Mood_D == 1 |
                                Substance_C == 1 & OCD_P == 1 |
                                Substance_C == 1 & BPD_P == 1 |
                                Substance_C == 1 & Substance_D == 1 |
                                Substance_C == 1 & Trauma_D == 1 |
                                Substance_C == 1 & Eating_D ==1 |
                                Substance_C == 1 & Anxiety_D ==1 |
                                Substance_C == 1 & Somatic_D ==1 |
                                Substance_C == 1 & Psychotic_D ==1, 1, 0)),
                 Co_Trauma = as.factor(
                    ifelse(Trauma_C == 1 & Mood_D == 1 |
                                Trauma_C == 1 & OCD_P == 1 |
                                Trauma_C == 1 & BPD_P == 1 |
                                Trauma_C == 1 & Substance_D == 1 |
                                Trauma_C == 1 & Eating_D ==1 |
                                Trauma_C == 1 & Anxiety_D ==1 |
                                Trauma_C == 1 & Somatic_D ==1 |
                                Trauma_C == 1 & Psychotic_D ==1, 1, 0))
  )

@@

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")

############.          Extract pre/post scores.   ######################

@@

    # Depressiopn
    CUDOS_Score_post <-  select(Mothership_post, dummy,Day1_CUDOS:Day40_CUDOS)
    # Anxiety
    CUXOS_Score_post <- select(Mothership_post, dummy,Day1_CUXOS:Day40_CUXOS)

@@

    #4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
           CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
           CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
        CUDOS_pre = BL_CUDOS,
        CUXOS_pre = BL_CUXOS,
        CUDOS_post = ifelse(!is.na(SUMdep_DC), SUMdep_DC,Post_Dep),
            CUDOS_post = ifelse(CUDOS_post < 0, NA, CUDOS_post),
        CUXOS_post = ifelse(!is.na(SUManx_DC), SUManx_DC,Post_anx),
            CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
                               ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
                                      ))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                           ifelse(BL_CUXOS > 20, "Sig Anx",
                           ifelse(BL_CUDOS > 20, "Sig Dep",
                           ifelse(is.na(BL_CUXOS),NA,
                           ifelse(is.na(BL_CUDOS),NA, "Sub Both"
                        )))))),
        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
                               ifelse(is.na(BL_CUXOS),NA, "Subclinical"
                              ))),
        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
                               ifelse(is.na(BL_CUDOS),NA, "Subclinical"
                              ))),
        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
                               ifelse(is.na(CUXOS_post),NA, "Subclinical"
                              ))),
        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
                               ifelse(is.na(CUDOS_post),NA, "Subclinical"
                              ))),
        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
                               ifelse(is.na(BL_CUXOS),NA,
                               ifelse(is.na(BL_CUDOS),NA, "Sub"
                               )))),
        Any_Sig_Post = as.factor(ifelse(CUXOS_post > 20 | CUDOS_post > 20, "Sig",
                               ifelse(is.na(CUXOS_post),NA,
                               ifelse(is.na(CUDOS_post),NA, "Sub"
                               )))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                 ifelse(BL_CUXOS > 20, "Sig Anx",
                 ifelse(BL_CUDOS > 20, "Sig Dep",
                 ifelse(is.na(BL_CUDOS), NA,
                 ifelse(is.na(BL_CUXOS), NA, "Subclinical"
                        )))))),
        Sig_Post = as.factor(ifelse(CUXOS_post > 20 & CUDOS_post > 20, "Sig Both",
                 ifelse(CUXOS_post > 20, "Sig Anx",
                 ifelse(CUDOS_post > 20, "Sig Dep",
                 ifelse(is.na(CUDOS_post), NA,
                 ifelse(is.na(CUXOS_post), NA, "Subclinical"
                        )))))),
        Sig_unresponse_type = as.factor(ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post == "Subclinical", "Responder",
                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Both", "Non-responder",
                            ifelse(Sig_BL == "Sig Anx" & Sig_Post == "Sig Anx", "Non-responder",
                            ifelse(Sig_BL == "Sig Dep" & Sig_Post == "Sig Dep", "Non-responder",
                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Anx", "Dep gone Anx not",
                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Dep", "Anx gone Dep not", 
                            ifelse(ifelse(Sig_BL == "Subclinical" & Sig_Post == "Subclinical", "Low_BL",       
                                   NA
        Sig_unresponse = as.factor(ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post == "Subclinical", "Responder",
                                        ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post %in% c("Sig Both","Sig Anx","Sig Dep"), "Non-responder",
                                        ifelse(ifelse(Sig_BL == "Subclinical" & Sig_Post == "Subclinical", "Low_BL",       
                                   NA
                                   ))))),

              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
                                 ifelse(BL_CUDOS > 45, "Severe",
                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
                                )))))),
        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
                                 ifelse(BL_CUXOS > 45, "Severe",
                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
                                )))))),
        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
                                 ifelse(CUDOS_post > 45, "Severe",
                                 ifelse(is.na(CUDOS_post), NA, "Remission"
                                )))))),
        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
                                 ifelse(CUXOS_post > 45, "Severe",
                                 ifelse(is.na(CUXOS_post), NA, "Remission"
                                )))))))

############                       Responder                   ############ 
#devtools::install_github("AWKruijt/JT-RCI")

@@

#devtools::install_github("zieglema/ClinicalSig")

RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

>>>>

---
title: "Lasso_RCI_Response"
author: Troy Hubert
output: html_document
date: "2024-01-28"
---

@@

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
head(df)

# source("~/Desktop/Coding/R working directory/Hospital_Visualizations/Lasso_RCI_Source.R")
```

## Clean, update, and wrangle data

The code below reads in the data frame, and prepares df for analysis.

this includes:
  1 Re-coding / Renaming variables
  2 Creating new Diagnostic variables 
  3 Functions to create Pre - post scores 
  4 RCI Analysis categorization
  5 Pre - Post long data sets

```{r}
# 1. Re-coding / Renaming variables ------------------------------------------
# We can change the current variables to make them easier to interpret.

#recode varaibles
Mothership <- mutate(Mothership, 
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                          "0"="<Grade 12",
                                          "1"="<Grade 12",
                                          "2"="HS Diploma or GED",
                                          "3"="HS Diploma or GED",
                                          "4"="Some College/Associates Degree",
                                          "5"="Some College/Associates Degree",
                                          "6"="Bachelors Degree",
                                          "7"="Bachelors Degree",
                                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                                       "0"="Female",
                                       "1"="Male",
                                       "2"="Non-Binary",
                                       "3"="Other",
                                       "4"="Other"),
                     Relationship_1 = ifelse(Relationship_1 == 8, NA, Relationship_1),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                                             "0"="Married or Cohabitating",
                                             "1"="Married or Cohabitating",
                                             "2"="Widowed or Separated",
                                             "3"="Widowed or Separated",
                                             "4"="Divorced",
                                             "5"="Single or Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                                          "1"="Straight",
                                          "2"="Gay",
                                          "3"="Bisexual",
                                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                                          "0"="General",
                                          "1"="Trauma",
                                          "2"="Young Adult",
                                          "3"="BPD"),
                     Race_1 = ifelse(Race_1 == 6, NA, Race_1),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                          "1" ="Treatment Complete",
                                          "2" ="Treatment nearly complete",
                                          "3" ="Insurance no longer covering",
                                          "4" ="Nonattendance",
                                          "5" ="Inappropriate (language)/Referred to another tx setting",
                                          "6" ="Transferred to inpatient",
                                          "7" ="Withdrew due to external limitations",
                                          "8"= "Withdrew AMA",
                                          "9"= "Other",
                                          "10"="Other",
                                          "0" ="Other"),
                     Referral_1 = as.factor(Referral_1),
                     Referral_1 = recode(Referral_1,
                                         "1" ="Inpatient",
                                         "2" ="PHP",
                                         "3" ="APS",
                                         "4" ="Psychatrist",
                                         "5" ="PCP",
                                         "6" ="Another Physican",
                                         "7" ="Therapist",
                                         "17"="Other",
                                         "0" ="Other"),

@@

# 2. Creating new diagnostic variables  -----------------------------------

@@

    # co occuring disorders
    Co_Anx = as.factor(
      ifelse(Anxiety_C == 1 & Mood_D == 1 |
               Anxiety_C == 1 & OCD_P == 1 |
               Anxiety_C == 1 & BPD_P == 1 |
               Anxiety_C == 1 & Substance_D == 1 |
               Anxiety_C == 1 & Trauma_D == 1 |
               Anxiety_C == 1 & Eating_D ==1 |
               Anxiety_C == 1 & Psychotic_D ==1 |
               Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Mood = as.factor(
      ifelse(Mood_C == 1 & Anxiety_D == 1 |
               Mood_C == 1 & OCD_P == 1 |
               Mood_C == 1 & BPD_P == 1 |
               Mood_C == 1 & Substance_D == 1 |
               Mood_C == 1 & Trauma_D == 1 |
               Mood_C == 1 & Eating_D ==1 |
               Mood_C == 1 & Psychotic_D ==1 |
               Mood_C == 1 & Somatic_D==1 , 1, 0)),
    Co_OCD = as.factor(
      ifelse(OCD_C == 1 & Anxiety_D == 1 |
               OCD_C == 1 & Mood_D == 1 |
               OCD_C == 1 & BPD_P== 1 |
               OCD_C == 1 & Substance_D == 1 |
               OCD_C == 1 & Trauma_D == 1 |
               OCD_C == 1 & Eating_D ==1 |
               OCD_C == 1 & Psychotic_D ==1 |
               OCD_C == 1 & Somatic_D ==1, 1, 0)),
    Co_BPD = as.factor(
      ifelse(BPD_C == 1 & Anxiety_D == 1 |
               BPD_C == 1 & Mood_D == 1 |
               BPD_C == 1 & OCD_P== 1 |
               BPD_C == 1 & Substance_D == 1 |
               BPD_C == 1 & Trauma_D == 1 |
               BPD_C == 1 & Eating_D ==1 |
               BPD_C == 1 & Psychotic_D ==1 |
               BPD_C == 1 & Somatic_D ==1 , 1, 0)),
    Co_Psychotic = as.factor(
      ifelse(Psychotic_C == 1 & Mood_D == 1 |
               Psychotic_C == 1 & OCD_P == 1 |
               Psychotic_C == 1 & BPD_P == 1 |
               Psychotic_C == 1 & Substance_D == 1 |
               Psychotic_C == 1 & Trauma_D == 1 |
               Psychotic_C == 1 & Eating_D ==1 |
               Psychotic_C == 1 & Anxiety_D ==1 |
               Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Eating = as.factor(
      ifelse(Eating_C == 1 & Mood_D == 1 |
               Eating_C == 1 & OCD_P == 1 |
               Eating_C == 1 & BPD_P == 1 |
               Eating_C == 1 & Substance_D == 1 |
               Eating_C == 1 & Trauma_D == 1 |
               Eating_C == 1 & Psychotic_D ==1 |
               Eating_C == 1 & Anxiety_D ==1 |
               Eating_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Somatic =  as.factor(
      ifelse(Somatic_C == 1 & Mood_D == 1 |
               Somatic_C == 1 & OCD_P == 1 |
               Somatic_C == 1 & BPD_P == 1 |
               Somatic_C == 1 & Substance_D == 1 |
               Somatic_C == 1 & Trauma_D == 1 |
               Somatic_C == 1 & Eating_D ==1 |
               Somatic_C == 1 & Anxiety_D ==1 |
               Somatic_C == 1 & Substance_D ==1 |
               Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Substance = as.factor(
      ifelse(Substance_C == 1 & Mood_D == 1 |
               Substance_C == 1 & OCD_P == 1 |
               Substance_C == 1 & BPD_P == 1 |
               Substance_C == 1 & Substance_D == 1 |
               Substance_C == 1 & Trauma_D == 1 |
               Substance_C == 1 & Eating_D ==1 |
               Substance_C == 1 & Anxiety_D ==1 |
               Substance_C == 1 & Somatic_D ==1 |
               Substance_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Trauma = as.factor(
      ifelse(Trauma_C == 1 & Mood_D == 1 |
               Trauma_C == 1 & OCD_P == 1 |
               Trauma_C == 1 & BPD_P == 1 |
               Trauma_C == 1 & Substance_D == 1 |
               Trauma_C == 1 & Eating_D ==1 |
               Trauma_C == 1 & Anxiety_D ==1 |
               Trauma_C == 1 & Somatic_D ==1 |
               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
  )

@@

# 3. Functions to create Pre - post scores -----------------------------------

@@

  # Depression
    CUDOS_Score_post <-  select(Mothership_post, dummy,Day1_CUDOS:Day40_CUDOS)
  # Anxiety
    CUXOS_Score_post <- select(Mothership_post, dummy,Day1_CUXOS:Day40_CUXOS)

@@

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
        CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
        CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
        CUDOS_pre = BL_CUDOS,
        CUXOS_pre = BL_CUXOS,
        CUDOS_post = ifelse(!is.na(SUMdep_DC), SUMdep_DC,Post_Dep),
        CUDOS_post = ifelse(CUDOS_post < 0, NA, CUDOS_post),
        CUXOS_post = ifelse(!is.na(SUManx_DC), SUManx_DC,Post_anx),
        CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
#5 Making some other varaibles
        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
                                      ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
                                      ))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUXOS),NA,
                                                       ifelse(is.na(BL_CUDOS),NA, "Sub Both"
                                                       )))))),
        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
                                      ifelse(is.na(BL_CUXOS),NA, "Subclinical"
                                      ))),
        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
                                      ifelse(is.na(BL_CUDOS),NA, "Subclinical"
                                      ))),
        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
                                        ifelse(is.na(CUXOS_post),NA, "Subclinical"
                                        ))),
        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
                                        ifelse(is.na(CUDOS_post),NA, "Subclinical"
                                        ))),
        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
                                      ifelse(is.na(BL_CUXOS),NA,
                                             ifelse(is.na(BL_CUDOS),NA, "Sub"
                                             )))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUDOS), NA,
                                                       ifelse(is.na(BL_CUXOS), NA, "Subclinical"
                                                       ))))))
)

# 4. RCI Analysis categorization ------------------------------------------

#devtools::install_github("AWKruijt/JT-RCI")

@@

#devtools::install_github("zieglema/ClinicalSig")
#1. Create df for RCI
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have data
  filter(!is.na(Days_complete_1)) |>
  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

#2. Left join data from the RCI dataset into the Mothership_post df
Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    )),
    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    )),
    RESPONDER_FIGS = as.factor(
      ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
             ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
      ))) |>
  filter(!is.na(RESPONDER_FIGS))
